Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
nobs

The effect of seasonality of resources on sociality can be directly measured by
differences across discrete time windows. Using an ordinal multilayer network
consisting of 20 discrete time windows throughout the study period, we observed
periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
Edge overlap was higher between approximately October and May
(time windows 1, 6-11, 15-20) compared to between approximately May and October
(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
overlap correspond to seasons of low resource availability [Peigner_2019].
Similarly, individual graph strength was also highest in these periods (Figure
\@ref(fig:temp) B).

@@

Finally, it is crucial to consider sufficient data to construct robust networks
when selecting time windows and study periods.

Conversely, picking the proper temporal scale is important but a challenge
because all layers in the multilayer network should reflect the same time
period, and the period should be long enough for each layer to have enough data
for robust networks [@Farine_2017]. These considerations may be limiting factors
when answering questions that require time frames that are relevant to different
individuals, for instance. In both mono- and multilayer networks, the effect of
scale on the relationship between an individual’s social network position and
fitness need to be considered based on the hypotheses being tested and
logistical constraints.

These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

>>>>

The effect of seasonality of resources on sociality can be directly measured by
differences across discrete time windows. Using an ordinal multilayer network
consisting of 20 discrete time windows throughout the study period, we observed
periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
Edge overlap was higher between approximately October and May
(time windows 1, 6-11, 15-20) compared to between approximately May and October
(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
overlap correspond to seasons of low resource availability [Peigner_2019].
Similarly, individual graph strength was also highest in these periods (Figure
\@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
in separate layers, multilayer networks provide a detailed and dynamic perspective at
animal social networks.

@@

Finally, it is crucial to consider sufficient data to construct robust networks
when selecting time windows and study periods. Time windows should be long
enough for each layer to have enough data for robust networks [@Farine_2017]. To
test the influence of data quantity on multilayer networks, we used a subset of
observations to generate multilayer networks. All network metrics across all
three habitat layers appeared to stabilize with increasing number of
observations. Individual graph strength showed high variability at low number of
observations, while edge overlap and multidegree increased sharply. After
approximately 200 observations, the rate of change for all metrics decreased and
and graph strength remained relatively static, while edge overlap and
multidegree continued to increase slowly. As more observations were added, more
and rarer relationships were recorded revealing the value of this form of
sensitivity analysis.

<!-- First, to what degree does the social scale of relationships, spatial -->
<!-- scale of landscapes, and temporal scale of analysis influence our ability to -->
<!-- interpret complex social systems?  -->
<!-- Second, can variation in the social, spatial, -->
<!-- and temporal scale improve predictions associated with biological differences in -->
<!-- seasonal resource availability and social association?  -->
